A Study on Common Bug Fix Patterns in Rust

### 2022-10-29 main.tex
abstract

\begin{abstract}
Insert your abstract here. Include keywords, PACS and mathematical
subject classification numbers as needed.
\keywords{First keyword \and Second keyword \and More}
% \PACS{PACS code1 \and PACS code2 \and more}
\subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

>>>>

\begin{abstract}
    Rust is a relatively new programming language which allows programmers to write programs that have low-level control over resources, while still ensuring high-level safety guarantees (for programs written in safe Rust). Rust's ownership framework enables programs to meet these two seemingly-contradictory goals. The Rust compiler's Borrow-Checker component enforces the ownership framework requirements which ensure Rust's safety guarantees.

Rust is popular: as of 2022, it has ranked first, for the sixth consecutive year, in Stack Overflow's annual Developer Survey as the most-loved programming language. The number of Rust developers is growing as the need for faster and safer software increases.

Yet, to the best of our knowledge, no research has sought to identify the most pervasive bug fix patterns within Rust programs. In this project, using a novel program modelling method, we mined the top 18 most-starred Rust projects in Github to discover the most common bug fix patterns committed to their repositories. We analyzed 87,726 code changes drawn from 57,214 commits across these 18 projects. After clustering the code changes, and conducting a manual analysis, we discovered 19 groups of cross-project bug fix patterns, which we categorize as (1) general patterns and (2) borrow-checker-related patterns. We describe each of these patterns and their implications to automated program repair.
\keywords{First keyword \and Second keyword \and More}
% \PACS{PACS code1 \and PACS code2 \and more}
\subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}
